---
title: "Baseball Win Probability Simulation"
output: html_document
---

# Astros @ Padres Simulation
### by Ross Woleben

```{r setup, comment=""}
```

```{r include=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
```

```{r echo = FALSE}
pos <- read.csv("mlb_active_pos_players2.csv")
pit <- read.csv("mlb_active_pitchers2.csv")
#used to calculate league average obp for spreadsheet calculations
h <- pos$H[pos$Year=='2021']
ab <- pos$AB[pos$Year=='2021']
average_ba <- sum(h)/sum(ab)
pa <- pos$PA[pos$Year=='2021']

w <- pos$BB[pos$Year=='2021']
hbp <- pos$HBP[pos$Year=='2021']
sf <- pos$SF[pos$Year=='2021']

average_obp <- (sum(h)+sum(w)+sum(hbp))/(sum(ab)+sum(w)+sum(hbp)+sum(sf))


total_singles <- (pos$H[pos$Year=='2021']-pos$X2B[pos$Year=='2021']-pos$X3B[pos$Year=='2021']-pos$HR[pos$Year=='2021'])
total_doubles <- pos$X2B
total_triples <- pos$X3B
total_hr <- pos$HR

average_single_rate <- sum(total_singles)/(sum(pa)-sum(ab)+sum(h))
average_double_rate <- sum(total_doubles)/(sum(pa)-sum(ab)+sum(h))
average_triple_rate <- sum(total_triples)/(sum(pa)-sum(ab)+sum(h))
average_hr_rate <- sum(total_hr)/(sum(pa)-sum(ab)+sum(h))
average_walk_rate <- 1-(average_single_rate+average_double_rate+average_triple_rate+average_hr_rate)

batters_faced <- pit$batters_faced[pit$Year=='2021']
so <- pit$SO[pit$Year=='2021']

so_rate <- sum(so)/sum(batters_faced)

at_bat <- function(pitcher_name, hitter_name, home_hitter=TRUE){
  
  hitter_found <- TRUE
  pitcher_found <- TRUE
  
  if(length(pit$player.name[pit$player.name==pitcher_name])==0){
    pitcher_found <- FALSE
  }else if(as.numeric(pit$IP[pit$player.name==pitcher_name])<10){
    pitcher_found <- FALSE
  }
  
  if(length(pos$player.name[pos$player.name==hitter_name])==0){
    hitter_found <- FALSE
  }
  
  
  
  if(pitcher_found==TRUE){
    if(hitter_found==TRUE){
      obp_chance <-  pos$OBP[pos$Year=='2021' & pos$player.name==hitter_name]*as.numeric(pit$OBPM[pit$Year=='2021' & pit$player.name==pitcher_name])
    }else{
      obp_chance <- average_obp * as.numeric(pit$OBPM[pit$Year=='2021' & pit$player.name==pitcher_name])
    }
  }else{
    if(hitter_found==TRUE){
      obp_chance <- pos$OBP[pos$Year=='2021' & pos$player.name==hitter_name]
    }else{
      obp_chance <- average_obp
    }
  }
  
  if(home_hitter==TRUE){
    obp_chance <- obp_chance * 1.024
  }else{
    obp_chance <- obp_chance * .976
  }
  
  val <- runif(1)
  outcome <- runif(1)
  
  if(val <= obp_chance){
    
    #Cleaning up on base outcomes
    if(hitter_found==TRUE){ #use hitters stats
      walk <- as.numeric(pos$Walk_percent[pos$Year=='2021' & pos$player.name==hitter_name])
      single <- walk + as.numeric(pos$Single_percent[pos$Year=='2021' & pos$player.name==hitter_name])
      double <- single + as.numeric(pos$Double_percent[pos$Year=='2021' & pos$player.name==hitter_name])
      triple <- double + as.numeric(pos$triple_percent[pos$Year=='2021' & pos$player.name==hitter_name])
      hr <- triple + as.numeric(pos$HR_percent[pos$Year=='2021' & pos$player.name==hitter_name])
    }else{ #use league average stats
      walk <- average_walk_rate
      single <- walk + average_single_rate
      double <- single + average_double_rate
      triple <- double + average_triple_rate
      hr <- triple + average_hr_rate
    }
    
    if(outcome<=walk){
      return("Walk")
    }else if(outcome<=single){
      return("Single")
    }else if(outcome<=double){
      return("Double")
    }else if(outcome<=triple){
      return("Triple")
    }else if(outcome<= hr){
      return("Home Run")
    }
    
  }else{
    #possible out - outcomes
    
    if(pitcher_found==TRUE){
      sor <- round(as.numeric(pit$SO_rate[pit$Year=='2021'& pit$player.name==pitcher_name])/so_rate/(1-obp_chance),3)
    }else{
      sor <- round(1/(1-obp_chance),3)
    }
    
    #https://library.fangraphs.com/pitching/batted-ball/
    #^ league average distribution of batted balls and expected averages (for 2010 so a bit)
    #ld: .21 with .685 average
    #gb: .44 with .239 average
    #fb: .24 with .207 average
    #iffb: .11
    so <- sor*.231
    go <- so+.5039*(1-so)
    ld <- go+.0996*(1-so)
    fb <- ld+.2865*(1-so)
    iffb <- fb+.11*(1-so)
    
    if(outcome <= so){
      return("Strikeout")
    }else if(outcome<=go){
      return("Groundout")
    }else if(outcome<=ld){
      return("Lineout")
    }else if(outcome<=fb){
      return("Flyout")
    }else if(outcome<=iffb){
      return("Pop Up")
    }
  }
  
}

print_score_vec <-function(vector){
  for(i in 1:length(vector)){
    if(i>9){
      cat(paste('', vector[i],''))
    }else{
      cat(paste(vector[i], ''))
    }
  }
}

innings_pitched <- function(outs){
  whole_inning <- floor(outs/3)
  partial_inning <- 0
  if(round(outs/3-whole_inning,1)==.3){
    partial_inning <- .1
  }else if(round(outs/3-whole_inning,1)==.7){
    partial_inning <- .2
  }
  inning <- whole_inning + partial_inning
  return(inning)
}

print_pitching_stats <- function(home_team_lineup, away_team_lineup){
  cat(home_team_lineup[[2]][1]); cat(": "); cat(innings_pitched(as.numeric(home_team_lineup[[2]][2]))); cat(" IP  "); cat(home_team_lineup[[2]][3]); cat(" ER  "); 
  cat(home_team_lineup[[2]][4]); cat(" H  "); cat(home_team_lineup[[2]][5]); cat(" BB  "); cat(home_team_lineup[[2]][6]); cat(" K\n");
  
  for(i in 1:length(home_team_lineup[[4]])){
    if(home_team_lineup[[4]][[i]][2] != 0 | home_team_lineup[[4]][[i]][3] != 0 | home_team_lineup[[4]][[i]][4] != 0 | home_team_lineup[[4]][[i]][5] != 0 | home_team_lineup[[4]][[i]][6] != 0){
      cat(home_team_lineup[[4]][[i]][1]); cat(": "); cat(innings_pitched(as.numeric(home_team_lineup[[4]][[i]][2]))); cat(" IP  "); cat(home_team_lineup[[4]][[i]][3]); cat(" ER  "); 
      cat(home_team_lineup[[4]][[i]][4]); cat(" H  "); cat(home_team_lineup[[4]][[i]][5]); cat(" BB  "); cat(home_team_lineup[[4]][[i]][6]); cat(" K\n");
    }
  }
  
  if(home_team_lineup[[5]][2]!=0 | home_team_lineup[[5]][3]!=0 | home_team_lineup[[5]][4]!=0 | home_team_lineup[[5]][5]!=0 | home_team_lineup[[5]][6]!=0){
    cat(home_team_lineup[[5]][1]); cat(": "); cat(innings_pitched(as.numeric(home_team_lineup[[5]][2]))); cat(" IP  "); cat(home_team_lineup[[5]][3]); cat(" ER  "); 
    cat(home_team_lineup[[5]][4]); cat(" H  "); cat(home_team_lineup[[5]][5]); cat(" BB  "); cat(home_team_lineup[[5]][6]); cat(" K\n");
  }
  
  
  cat(away_team_lineup[[2]][1]); cat(": "); cat(innings_pitched(as.numeric(away_team_lineup[[2]][2]))); cat(" IP  "); cat(away_team_lineup[[2]][3]); cat(" ER  "); 
  cat(away_team_lineup[[2]][4]); cat(" H  "); cat(away_team_lineup[[2]][5]); cat(" BB  "); cat(away_team_lineup[[2]][6]); cat(" K\n");
  
  for(i in 1:length(away_team_lineup[[4]])){
    if(away_team_lineup[[4]][[i]][2] != 0 | away_team_lineup[[4]][[i]][3] != 0 | away_team_lineup[[4]][[i]][4] != 0 | away_team_lineup[[4]][[i]][5] != 0 | away_team_lineup[[4]][[i]][6] != 0){
      cat(away_team_lineup[[4]][[i]][1]); cat(": "); cat(innings_pitched(as.numeric(away_team_lineup[[4]][[i]][2]))); cat(" IP  "); cat(away_team_lineup[[4]][[i]][3]); cat(" ER  "); 
      cat(away_team_lineup[[4]][[i]][4]); cat(" H  "); cat(away_team_lineup[[4]][[i]][5]); cat(" BB  "); cat(away_team_lineup[[4]][[i]][6]); cat(" K\n");
    }
  }
  if(away_team_lineup[[5]][2]!=0 | away_team_lineup[[5]][3]!=0 | away_team_lineup[[5]][4]!=0 | away_team_lineup[[5]][5]!=0 | away_team_lineup[[5]][6]!=0){
    cat(away_team_lineup[[5]][1]); cat(": "); cat(innings_pitched(as.numeric(away_team_lineup[[5]][2]))); cat(" IP  "); cat(away_team_lineup[[5]][3]); cat(" ER  "); 
    cat(away_team_lineup[[5]][4]); cat(" H  "); cat(away_team_lineup[[5]][5]); cat(" BB  "); cat(away_team_lineup[[5]][6]); cat(" K\n");
  }
  
  
}

#currently broken for some reason
print_batting_stats <- function(team_batting_stats, team_score){
  for(i in 1:length(team_batting_stats)){ #1-9
    hit_count <- 0
    out_count <- 0
    double_count <- 0
    triple_count <- 0
    hr_count <- 0
    walk_count <- 0
    rbi <- team_batting_stats[[i]][2]
    hits_string <- ""
    for(j in 3:length(team_batting_stats[[i]])){
      #print(away_team_batting_stats[[i]][j])
      if(team_batting_stats[[i]][j]=='Single'| team_batting_stats[[i]][j]=='Double'|team_batting_stats[[i]][j]=='Triple'|team_batting_stats[[i]][j]=='Home Run'){
        hit_count <- hit_count+1
        if(team_batting_stats[[i]][j]=='Home Run'){
          hr_count <- hr_count+1
        }
        if(team_batting_stats[[i]][j]=='Triple'){
          triple_count <- triple_count+1
        }
        if(team_batting_stats[[i]][j]=='Double'){
          double_count <- double_count+1
        }
        
      }else if(team_batting_stats[[i]][j]=="Walk"){
        walk_count <- walk_count+1
      }else{
        out_count<- out_count+1
      }
    }
    if(hr_count>0){
      if(hr_count>1){
        hits_string <- paste(hr_count, "HR,")
      }else{
        hits_string <- "HR,"
      }
    }
    if(rbi>0){
      if(rbi>1){
        if(double_count>=1 | triple_count >=1){
          hits_string <- paste(hits_string, rbi, "RBI,")
        }else{
          hits_string <- paste(hits_string, rbi, "RBI")
        }
        
      }else{
        if(double_count>=1 | triple_count >=1){
          hits_string <- paste(hits_string, "RBI,")
        }else{
          hits_string <- paste(hits_string, "RBI")
        }
        
      }
      
    }
    if(triple_count>0){
      if(triple_count>1){
        if(double_count>=1){
          hits_string <- paste(hits_string, triple_count, "Triple,")
        }else{
          hits_string <- paste(hits_string, triple_count, "Triple")
        }
        
      }else{
        if(double_count>=1){
          hits_string <- paste(hits_string, "Triple,")
        }else{
          hits_string <- paste(hits_string, "Triple")
        }
        
      }
    }
    if(double_count>0){
      if(double_count>1){
        hits_string <- paste(hits_string, double_count, "Double")
      }else{
        hits_string <- paste(hits_string, "Double")
      }
    }
    if(hit_count==0 & walk_count>=1){
      if(walk_count>1){
        hits_string <- paste(walk_count, "BB")
      }else{
        hits_string <- paste("BB")
      }
    }
    if(rbi>0){
      cat(paste(team_batting_stats[[i]][1], gsub(" ","", paste(hit_count, "-", hit_count+out_count)), hits_string,"\n"))
    }else if(sum(team_score)==0 & (i==3|i==4)){
      cat(paste(team_batting_stats[[i]][1], gsub(" ","", paste(hit_count, "-", hit_count+out_count)), hits_string,"\n"))
    }
    
  }
}

print_box_score <- function(home_team_lineup, home_score, home_hits, home_lob, home_team_batting_stats, away_team_lineup, away_score, away_hits, away_lob,away_team_batting_stats){
  game_len = c(1:length(away_score))
  cat("Team\t| "); cat(game_len); cat("\t|  F\t H\tLOB\n")
  cat("----------------------------------------------------\n")
  cat(paste(away_team_lineup[[1]], "\t| ")); print_score_vec(away_score); cat("\t|  "); cat(sum(away_score)); cat("\t", away_hits, "\t", away_lob, "\n")
  cat("----------------------------------------------------\n")
  cat(paste(home_team_lineup[[1]], "\t| ")); print_score_vec(home_score); cat("\t|  "); cat(sum(home_score)); cat("\t", home_hits, "\t", home_lob, "\n")
  
  #need to add rbi and runs
  #print(away_team_batting_stats)
  print_pitching_stats(home_team_lineup, away_team_lineup)
  
  cat(away_team_lineup[[1]],":\n")
  print_batting_stats(away_team_batting_stats, away_score)
  cat(home_team_lineup[[1]],":\n")
  print_batting_stats(home_team_batting_stats, home_score)
  
}

base_runners <- function(ab_outcome, current_baserunners, outs){
  runs <- 0
  
  if(ab_outcome =='Groundout'){
    outs <- outs +1
    if(outs==3){
      return(list(runs, current_baserunners, outs)) 
    }else{ #play starts with 0 or 1 out
      if(current_baserunners[1]==T){
        dp_chance <- runif(1)
        if(dp_chance<=.7){ #70% chance for dp
          outs <- outs+1
          if(outs==3){
            return(list(runs, current_baserunners, outs))
          }else{
            if(current_baserunners[3]==T){
              runs <- runs+1
              current_baserunners[3]=F
            }
            if(current_baserunners[2]==T){
              current_baserunners[3]=T
              current_baserunners[2]=F
            }
          }
          current_baserunners[1]=F
        }else{
          if(current_baserunners[3]==T){
            runs <- runs+1
            current_baserunners[3]=F
          }
          if(current_baserunners[2]==T){
            current_baserunners[3]=T
            current_baserunners[2]=F
          }
        }
      }else{
        if(current_baserunners[3]==T){
          runs <- runs+1
          current_baserunners[3]=F
        }
        if(current_baserunners[2]==T){
          current_baserunners[3]=T
          current_baserunners[2]=F
        }
      }
    }
    
    return(list(runs, current_baserunners, outs)) 
  }
  if(ab_outcome=='Lineout'){
    if(outs==2){
      outs <- 3
    }else{ #0 or 1 outs
      if(current_baserunners[1]==T | current_baserunners[2]==T){
        dp_chance <- runif(1)
        if(dp_chance<=.02){ #2% chance for a double play
          if(current_baserunners[1]==T & current_baserunners[2]==T){
            first_or_second <- runif(1)
            if(first_or_second<=.5){
              current_baserunners[1]=F
            }else{
              current_baserunners[2]=F
            }
          }else{
            if(current_baserunners[1]==T){
              current_baserunners[1]=F
            }else{
              current_baserunners[2]=F
            }
          }
          
          outs <- outs+2
        }else{
          outs <- outs+1
        }
      }else{
        outs <- outs+1
      }
    }
    return(list(runs, current_baserunners, outs)) 
  }
  if(ab_outcome=='Flyout'){
    if(outs==2){
      outs <- 3
    }else{ #0 or 1 outs
      if(current_baserunners[2]==T|current_baserunners[3]==T){
        attempt_to_tag <- runif(1)
        if(current_baserunners[3]==T){
          if(attempt_to_tag<=.9){ #90% chance to tag up
            thrown_out <- runif(1)
            if(thrown_out <=.1){ #10% chance to be thrown out at home
              outs <- outs+2
              current_baserunners[3]=F
              if(current_baserunners[2]==T){
                current_baserunners[2]=F
                current_baserunners[3]=T
              }
            }else{
              runs <- runs+1
              current_baserunners[3]=F
              outs <- outs +1
            }
          }else{ #no tag up attempt
            outs <- outs +1
          }
        }else{ #there is only a runner on 2nd
          if(attempt_to_tag<=.6){ #60% chance to attempt to tag up
            thrown_out <- runif(1)
            if(thrown_out<=.15){ #15% chance to be thrown out at third
              outs <- outs+2
              current_baserunners[2]=F
            }else{
              current_baserunners[3]=T
              outs<-outs+1
            }
          }else{
            outs <- outs+1
          }
        }
      }else{
        outs <- outs +1
      }
    }
    return(list(runs, current_baserunners, outs)) 
  }
  if(ab_outcome=='Pop Up'|ab_outcome=='Strikeout'){
    outs <- outs+1
    return(list(runs, current_baserunners, outs)) 
  }
  
  if(ab_outcome=='Walk'){
    
    if(current_baserunners[1]==T){
      if(current_baserunners[2]==T){
        if(current_baserunners[3]==T){
          runs <- 1
        }else{
          current_baserunners[3]<-T
        }
      }else{
        current_baserunners[2]<-T
      }
    }else{
      current_baserunners[1]<-T
    }
    
  }else if(ab_outcome=='Single'){
    first_to_third <- runif(1)
    second_to_home <- runif(1)
    
    if(current_baserunners[3]==T){ #runner scores on single if they start on third
      current_baserunners[3]<-F
      runs <- runs+1
    }
    if(current_baserunners[2]==T){
      current_baserunners[2]<-F
      if(second_to_home<=.66){ #66% for runner to move from second to home on a single
        runs<-runs+1
      }else{ #40% for runner to move from second to third on single
        current_baserunners[3]<-T
      }
    }
    if(current_baserunners[1]==T){
      if(first_to_third<=.2 && current_baserunners[3]==F){ #20% runner makes it to third on a single if third is open
        current_baserunners[3]<-T
      }else{ #80% for runner to go from first to second on single
        current_baserunners[2]<-T
      } 
    }
    
    current_baserunners[1]<-T
    
  }else if(ab_outcome=='Double'){
    first_to_home <- runif(1)
    second_to_home <- runif(1)
    
    if(current_baserunners[3]==T){
      current_baserunners[3]<-F
      runs <- runs+1
    }
    
    if(current_baserunners[2]==T){
      if(second_to_home<=.01 && current_baserunners[1]==F){ #1% for runner to not score from second on double
        current_baserunners[3]<-T
      }else{
        runs<- runs+1
      }
      current_baserunners[2]<-F
    }
    
    if(current_baserunners[1]==T){
      if(first_to_home<=.47){ #47% for a runner to score from first on a double
        runs <- runs+1
      }else{
        current_baserunners[3]<- T
      }
      current_baserunners[1]<- F
    }
    
    current_baserunners[2]<-T
    
    
  }else if(ab_outcome=='Triple'){
    runs <- sum(current_baserunners)
    current_baserunners <- c(0,0,1)
  }else if(ab_outcome=='Home Run'){
    runs <- sum(current_baserunners)+1
    current_baserunners <- c(0,0,0)
  }
  
  
  return (list(runs, current_baserunners))
}

baseball_game <- function(home_team_lineup, away_team_lineup){
  win_percentages <- data.frame(team = character(), inning_no = numeric(), batters_faced=numeric(), home=numeric(), away=numeric(), at_bat_outcome = character())
  home_score <- c()
  away_score <- c()
  
  total_home_hits <- 0
  total_away_hits <- 0
  total_home_lob <- 0
  total_away_lob <- 0
  on_base <- c(F,F,F)
  current_home_pitcher <- 2
  current_away_pitcher <- 2
  home_reliever_index <- 1
  away_reliever_index <- 1
  home_reliever_outs <- 0
  away_reliever_outs <- 0
  top_inning <- TRUE
  total_batters_faced <- 0
  batters_this_inning <- 0
  
  runs <- 0 
  outs <- 0
  inning <- 1
  home_index <- 1
  away_index <- 1
  PA_text <- ""
  
  if(total_batters_faced==0){
    win_per <- win_prob_calc(win_percentages, home_team_lineup, away_team_lineup, home_score, away_score, on_base, current_home_pitcher, current_away_pitcher,
                             home_reliever_index, away_reliever_index, home_reliever_outs, away_reliever_outs,
                             inning, home_index, away_index, outs, total_batters_faced,sim_top_of_inning = top_inning)
    win_percentages <- win_percentages %>% add_row(team = away_team_lineup[[1]], inning_no = inning, batters_faced= total_batters_faced, home = win_per/1000, away = 1-(win_per/1000), at_bat_outcome = NULL)
  }
  
  while(TRUE){
    #print(paste("Top of Inning",inning))
    while(TRUE){
      if(inning>=10){
        on_base <- c(F,T,F)
      }
      
      
      
      if(current_home_pitcher==2){
        if(as.numeric(home_team_lineup[[2]][2])+as.numeric(home_team_lineup[[2]][4])+as.numeric(home_team_lineup[[2]][5]) >29 |
           as.numeric(home_team_lineup[[2]][3])>=6 | (innings_pitched(as.numeric(home_team_lineup[[2]][2]))/as.numeric(home_team_lineup[[2]][3]) <= .8 & inning >=5) |
           (innings_pitched(as.numeric(home_team_lineup[[2]][2]))/as.numeric(home_team_lineup[[2]][3]) <= .5 & inning >=7)){
          current_home_pitcher = 4
        }
      }else if(current_home_pitcher==5){
        if(as.numeric(home_team_lineup[[5]][3])>=2 | as.numeric(home_team_lineup[[5]][2])>=6 | as.numeric(home_team_lineup[[2]][4])+as.numeric(home_team_lineup[[2]][5]) >=4){
          current_home_pitcher = 4
        }
      }else if(current_home_pitcher==4){
        if(home_reliever_outs>=6 | home_team_lineup[[4]][[home_reliever_index]][3]>=2 | 
           as.numeric(home_team_lineup[[4]][[home_reliever_index]][4])+as.numeric(home_team_lineup[[4]][[home_reliever_index]][5])>=3){
          if(home_reliever_index+1 <= length(home_team_lineup[[4]])){
            home_reliever_index <- home_reliever_index+1
            home_reliever_outs <- 0
          }
        }
      }
      
      
      if((inning==9|inning==10) & sum(home_score)-sum(away_score)<=3 & sum(home_score)-sum(away_score)>=0 & as.numeric(home_team_lineup[[2]][2])+as.numeric(home_team_lineup[[2]][4])+as.numeric(home_team_lineup[[2]][5]) >29){
        current_home_pitcher = 5
      }
      
      #print(paste("inning", inning, "out",outs))
      if(current_home_pitcher==2 | current_home_pitcher==5){
        PA <- at_bat(home_team_lineup[[current_home_pitcher]][1],away_team_lineup[[3]][[away_index]][1])
      }else{
        PA <- at_bat(home_team_lineup[[4]][[home_reliever_index]][1],away_team_lineup[[3]][[away_index]][1])
      }
      total_batters_faced <- total_batters_faced + 1
      batters_this_inning <- batters_this_inning + 1
      
      if(length(away_team_lineup[[3]][[away_index]])==1){
        away_team_lineup[[3]][[away_index]]<-append(away_team_lineup[[3]][[away_index]],0)
      }
      away_team_lineup[[3]][[away_index]]<-append(away_team_lineup[[3]][[away_index]],PA)
      
      #print(paste("Batter: ", away_team_lineup[[3]][[away_index]][1], " in the ", away_index, "spot"))
      #print(PA)
      
      
      
      if(PA=='Strikeout'|PA=='Groundout'|PA=='Lineout'|PA=='Flyout'|PA=='Pop Up'){
        result <- base_runners(PA, on_base, outs)
        on_base < result[[2]]
        runs <- runs + result[[1]]
        if(current_home_pitcher==2 | current_home_pitcher ==5){
          home_team_lineup[[current_home_pitcher]][2] <- as.numeric(home_team_lineup[[current_home_pitcher]][2]) + result[[3]]-outs
        }else{
          home_team_lineup[[4]][[home_reliever_index]][2] <- as.numeric(home_team_lineup[[4]][[home_reliever_index]][2]) + result[[3]]-outs
          home_reliever_outs <- home_reliever_outs + result[[3]]-outs
        }
        
        outs <- result[[3]]
        #print(paste("OUTS:", outs))
        if(PA=='Strikeout'){
          if(current_home_pitcher==2 | current_home_pitcher==5){
            home_team_lineup[[current_home_pitcher]][6] <- as.numeric(home_team_lineup[[current_home_pitcher]][6]) + 1
          }else{
            home_team_lineup[[4]][[home_reliever_index]][6] <- as.numeric(home_team_lineup[[4]][[home_reliever_index]][6]) + 1
          }
          
        }
        
        
        
      }else{
        result <-base_runners(PA, on_base,outs)
        on_base <- result[[2]]
        runs <- runs+ result[[1]]
        if(PA=='Walk'){
          if(current_home_pitcher==2 | current_home_pitcher ==5){
            home_team_lineup[[current_home_pitcher]][5] <- as.numeric(home_team_lineup[[current_home_pitcher]][5]) + 1
          }else{
            home_team_lineup[[4]][[home_reliever_index]][5] <- as.numeric(home_team_lineup[[4]][[home_reliever_index]][5]) + 1
          }
          
        }else{
          if(current_home_pitcher==2 | current_home_pitcher ==5){
            home_team_lineup[[current_home_pitcher]][4] <- as.numeric(home_team_lineup[[current_home_pitcher]][4]) + 1
          }else{
            home_team_lineup[[4]][[home_reliever_index]][4] <- as.numeric(home_team_lineup[[4]][[home_reliever_index]][4]) + 1
          }
          
          total_away_hits <- total_away_hits+1
        }
        
      }
      
      
      
      #add any ER to pitcher
      if(current_home_pitcher==2 | current_home_pitcher ==5){
        home_team_lineup[[current_home_pitcher]][3] <- as.numeric(home_team_lineup[[current_home_pitcher]][3]) + result[[1]]
      }else{
        home_team_lineup[[current_home_pitcher]][[home_reliever_index]][3] <- as.numeric(home_team_lineup[[current_home_pitcher]][[home_reliever_index]][3]) + result[[1]]
      }
      
      #determine if you need to switch out pitcher
      
      #add stats to hitter
      away_team_lineup[[3]][[away_index]][2]<- as.numeric(away_team_lineup[[3]][[away_index]][2])+result[[1]]
      
      
      if(away_index==9){
        away_index <- 1
      }else{
        away_index <- away_index+1
      }
      
      win_per <- win_prob_calc(win_percentages, home_team_lineup, away_team_lineup, home_score, c(away_score,runs), on_base, current_home_pitcher, current_away_pitcher,
                               home_reliever_index, away_reliever_index, home_reliever_outs, away_reliever_outs,
                               inning, home_index, away_index, outs, total_batters_faced,sim_top_of_inning = top_inning)
      if(result[[1]] >= 1){
        PA_text <- paste(result[[1]], "run", PA)
      }
      win_percentages <- win_percentages %>% add_row(team = away_team_lineup[[1]], inning_no = inning, batters_faced= total_batters_faced, home = win_per/1000, away = 1-(win_per/1000), at_bat_outcome = PA_text)
      PA_text <- ""
      
      if(outs==3){
        away_score <- append(away_score, runs)
        runs <- 0
        outs <- 0
        total_away_lob <- total_away_lob + sum(on_base)
        on_base <- c(F,F,F)
        top_inning <- FALSE
        break
      }
      
      
    }
    
    if(inning==9 & sum(home_score)>sum(away_score)){
      break
    }
    
    
    #print(paste("Bottom of Inning", inning))
    while(TRUE){
      if(inning>=10){
        on_base <- c(F,T,F)
      }
      
      
      
      if(current_away_pitcher==2){
        if(as.numeric(away_team_lineup[[2]][2])+as.numeric(away_team_lineup[[2]][4])+as.numeric(away_team_lineup[[2]][5]) >29 |
           as.numeric(away_team_lineup[[2]][3])>=6 | (innings_pitched(as.numeric(away_team_lineup[[2]][2]))/as.numeric(away_team_lineup[[2]][3]) <= .8 & inning >=5) |
           (innings_pitched(as.numeric(away_team_lineup[[2]][2]))/as.numeric(away_team_lineup[[2]][3]) <= .5 & inning >=7)){
          current_away_pitcher = 4
        }
      }else if(current_away_pitcher==5){
        if(as.numeric(away_team_lineup[[5]][3])>=2 | as.numeric(away_team_lineup[[5]][2])>=6 | as.numeric(away_team_lineup[[2]][4])+as.numeric(away_team_lineup[[2]][5]) >=4){
          current_away_pitcher = 4
        }
      }else if(current_away_pitcher==4){
        if(innings_pitched(as.numeric(away_team_lineup[[4]][[away_reliever_index]][2]))>=2 | away_team_lineup[[4]][[away_reliever_index]][3]>=2 | 
           as.numeric(away_team_lineup[[4]][[away_reliever_index]][4])+as.numeric(away_team_lineup[[4]][[away_reliever_index]][5])>=3){
          if(away_reliever_index+1 <= length(away_team_lineup[[4]])){
            away_reliever_index <- away_reliever_index+1
            away_reliever_outs <- 0
          }
        }
      }
      
      if((inning==9|inning==10) & sum(away_score)-sum(home_score)<=3 & sum(away_score)-sum(home_score)>0 & as.numeric(away_team_lineup[[2]][2])+as.numeric(away_team_lineup[[2]][4])+as.numeric(away_team_lineup[[2]][5])>0){
        current_away_pitcher = 5
      }
      
      if(current_away_pitcher==2|current_away_pitcher==5){
        PA <- at_bat(away_team_lineup[[current_away_pitcher]][1],home_team_lineup[[3]][[home_index]][1])
      }else{
        PA <- at_bat(away_team_lineup[[4]][[away_reliever_index]][1],home_team_lineup[[3]][[home_index]][1])
      }
      total_batters_faced <- total_batters_faced + 1
      batters_this_inning <- batters_this_inning + 1
      
      if(length(home_team_lineup[[3]][[home_index]])==1){
        home_team_lineup[[3]][[home_index]]<-append(home_team_lineup[[3]][[home_index]],0)
      }
      home_team_lineup[[3]][[home_index]]<-append(home_team_lineup[[3]][[home_index]],PA)
      
      #print(paste("Batter: ", home_team_lineup[[3]][[home_index]][1], " in the ", home_index, "spot"))
      #print(PA)
      
      
      
      if(PA=='Strikeout'|PA=='Groundout'|PA=='Lineout'|PA=='Flyout'|PA=='Pop Up'){
        result <- base_runners(PA, on_base, outs)
        on_base <- result[[2]]
        runs <- runs + result[[1]]
        if(current_away_pitcher==2 | current_away_pitcher==5){
          away_team_lineup[[current_away_pitcher]][2] <- as.numeric(away_team_lineup[[current_away_pitcher]][2]) + result[[3]]-outs
        }else{
          away_team_lineup[[4]][[away_reliever_index]][2] <- as.numeric(away_team_lineup[[4]][[away_reliever_index]][2]) + result[[3]]-outs
          away_reliever_outs <- away_reliever_outs + result[[3]]-outs
        }
        
        outs <- result[[3]]
        #print(paste("OUTS:", outs))
        if(PA=='Strikeout'){
          if(current_away_pitcher==2 | current_away_pitcher==5){
            away_team_lineup[[current_away_pitcher]][6] <- as.numeric(away_team_lineup[[current_away_pitcher]][6]) + 1
          }else{
            away_team_lineup[[4]][[away_reliever_index]][6] <- as.numeric(away_team_lineup[[4]][[away_reliever_index]][6]) + 1
          }
          
        }
        
      }else{
        result <-base_runners(PA, on_base,outs)
        
        on_base <- result[[2]]
        runs <- runs+ result[[1]]
        if(PA=='Walk'){
          if(current_away_pitcher==2 | current_away_pitcher==5){
            away_team_lineup[[current_away_pitcher]][5] <- as.numeric(away_team_lineup[[current_away_pitcher]][5]) + 1
          }else{
            away_team_lineup[[4]][[away_reliever_index]][5] <- as.numeric(away_team_lineup[[4]][[away_reliever_index]][5]) + 1
          }
          
        }else{
          if(current_away_pitcher==2 | current_away_pitcher==5){
            away_team_lineup[[current_away_pitcher]][4] <- as.numeric(away_team_lineup[[current_away_pitcher]][4]) + 1
          }else{
            away_team_lineup[[4]][[away_reliever_index]][4] <- as.numeric(away_team_lineup[[4]][[away_reliever_index]][4]) + 1
          }
          
          total_home_hits <- total_home_hits+1
        }
      }
      #update stats for pitcher
      if(current_away_pitcher==2 | current_away_pitcher==5){
        away_team_lineup[[current_away_pitcher]][3] <- as.numeric(away_team_lineup[[current_away_pitcher]][3]) + result[[1]]
      }else{
        away_team_lineup[[4]][[away_reliever_index]][3] <- as.numeric(away_team_lineup[[4]][[away_reliever_index]][3]) + result[[1]]
      }
      
      
      #determine if you need to switch out pitcher
      
      #update stats for hitter
      home_team_lineup[[3]][[home_index]][2]<- as.numeric(home_team_lineup[[3]][[home_index]][2])+result[[1]]
      
      if(home_index==9){
        home_index <- 1
      }else{
        home_index <- home_index+1
      }
      win_per <- win_prob_calc(win_percentages, home_team_lineup, away_team_lineup, c(home_score,runs), away_score, on_base, current_home_pitcher, current_away_pitcher,
                               home_reliever_index, away_reliever_index, home_reliever_outs, away_reliever_outs,
                               inning, home_index, away_index, outs, total_batters_faced,sim_top_of_inning = top_inning)
      if(result[[1]] >= 1){
        PA_text <- paste(result[[1]], "run", PA)
      }
      win_percentages <- win_percentages %>% add_row(team = home_team_lineup[[1]],inning_no = inning, batters_faced= total_batters_faced, home = win_per/1000, away = 1-(win_per/1000), at_bat_outcome = PA_text)
      PA_text <- ""
      if(outs==3 | ((sum(home_score)+runs)>sum(away_score)&inning>=9)){
        if(inning>=9 & (sum(home_score)+runs-sum(away_score))>1 & PA!='Home Run'){
          if(runs==3){
            runs<-2
            PA <- "Double"
          }else if(runs==2){
            if(inning>=10){
              PA <- "Single"
            }
            runs<-1
          }
        }
        home_score <- append(home_score, runs)
        runs <- 0
        outs <- 0
        
        total_home_lob <- total_home_lob + sum(on_base)
        on_base <- c(F,F,F)
        top_inning <- TRUE
        batters_this_inning <- 0
        break
      }
      
    }
    
    if(sum(away_score)!=sum(home_score) & inning >=9){
      break
    }
    
    inning <- inning +1
    
  }
  if(sum(home_score)>sum(away_score)){
    win_percentages <- win_percentages %>% add_row(team = NULL, inning_no = inning, batters_faced= total_batters_faced+1, home = 1, away = 0, at_bat_outcome = NULL)
  }else{
    win_percentages <- win_percentages %>% add_row(team = NULL, inning_no = inning, batters_faced= total_batters_faced+1, home = 0, away = 1, at_bat_outcome = NULL)
  }
  print_box_score(home_team_lineup,home_score,total_home_hits, total_home_lob, home_team_lineup[[3]], away_team_lineup, away_score, total_away_hits, total_away_lob, away_team_lineup[[3]])
  return(win_percentages)
}

win_prob_calc <- function(df, home_team_lineup, away_team_lineup, sim_home_score, sim_away_score, current_on_base, sim_current_home_pitcher, sim_current_away_pitcher, 
                          sim_home_reliever_index, sim_away_reliever_index, sim_home_reliever_outs, sim_away_reliever_outs, 
                          current_inning, sim_home_index, sim_away_index, current_outs, total_batters_faced, sim_top_of_inning = TRUE){
  wp_vec <- c()
  for(i in 1:1000){
    home_score <- c(sim_home_score)
    away_score <- c(sim_away_score)
    
    on_base <- current_on_base
    current_home_pitcher <- sim_current_home_pitcher
    current_away_pitcher <- sim_current_away_pitcher
    home_reliever_index <- sim_home_reliever_index
    away_reliever_index <- sim_away_reliever_index
    home_reliever_outs <- sim_home_reliever_index
    away_reliever_outs <- sim_away_reliever_outs
    
    runs <- 0 
    outs <- current_outs
    inning <- current_inning
    home_index <- sim_home_index
    away_index <- sim_away_index
    top_of_inning = sim_top_of_inning
    
    if(outs == 3){
      if(sim_top_of_inning==TRUE){
        top_of_inning <- FALSE
      }else{
        top_of_inning <- TRUE
      }
      outs <- 0
    }
    
    while(TRUE){
      #print(paste("Top of Inning",inning))
      if(top_of_inning==TRUE){
        while(TRUE){
          if(inning>=10){
            on_base <- c(F,T,F)
          }
          
          
          
          if(current_home_pitcher==2){
            if(as.numeric(home_team_lineup[[2]][2])+as.numeric(home_team_lineup[[2]][4])+as.numeric(home_team_lineup[[2]][5]) >29 |
               as.numeric(home_team_lineup[[2]][3])>=6 | (innings_pitched(as.numeric(home_team_lineup[[2]][2]))/as.numeric(home_team_lineup[[2]][3]) <= .8 & inning >=5) |
               (innings_pitched(as.numeric(home_team_lineup[[2]][2]))/as.numeric(home_team_lineup[[2]][3]) <= .5 & inning >=7)){
              current_home_pitcher = 4
            }
          }else if(current_home_pitcher==5){
            if(as.numeric(home_team_lineup[[5]][3])>=2 | as.numeric(home_team_lineup[[5]][2])>=6 | as.numeric(home_team_lineup[[2]][4])+as.numeric(home_team_lineup[[2]][5]) >=4){
              current_home_pitcher = 4
            }
          }else if(current_home_pitcher==4){
            if(home_reliever_outs>=6 | home_team_lineup[[4]][[home_reliever_index]][3]>=2 | 
               as.numeric(home_team_lineup[[4]][[home_reliever_index]][4])+as.numeric(home_team_lineup[[4]][[home_reliever_index]][5])>=3){
              if(home_reliever_index+1 <= length(home_team_lineup[[4]])){
                home_reliever_index <- home_reliever_index+1
                home_reliever_outs <- 0
              }
            }
          }
          
          
          if((inning==9|inning==10) & sum(home_score)-sum(away_score)<=3 & sum(home_score)-sum(away_score)>=0 & as.numeric(home_team_lineup[[2]][2])+as.numeric(home_team_lineup[[2]][4])+as.numeric(home_team_lineup[[2]][5]) >29){
            current_home_pitcher = 5
          }
          
          #print(paste("inning", inning, "out",outs))
          if(current_home_pitcher==2 | current_home_pitcher==5){
            PA <- at_bat(home_team_lineup[[current_home_pitcher]][1],away_team_lineup[[3]][[away_index]][1], home_hitter=FALSE)
          }else{
            PA <- at_bat(home_team_lineup[[4]][[home_reliever_index]][1],away_team_lineup[[3]][[away_index]][1],home_hitter=FALSE)
          }
          
          
          if(length(away_team_lineup[[3]][[away_index]])==1){
            away_team_lineup[[3]][[away_index]]<-append(away_team_lineup[[3]][[away_index]],0)
          }
          away_team_lineup[[3]][[away_index]]<-append(away_team_lineup[[3]][[away_index]],PA)
          
          #print(paste("Batter: ", away_team_lineup[[3]][[away_index]][1], " in the ", away_index, "spot"))
          #print(PA)
          
          
          
          if(PA=='Strikeout'|PA=='Groundout'|PA=='Lineout'|PA=='Flyout'|PA=='Pop Up'){
            result <- base_runners(PA, on_base, outs)
            on_base < result[[2]]
            runs <- runs + result[[1]]
            if(current_home_pitcher==2 | current_home_pitcher ==5){
              home_team_lineup[[current_home_pitcher]][2] <- as.numeric(home_team_lineup[[current_home_pitcher]][2]) + result[[3]]-outs
            }else{
              home_team_lineup[[4]][[home_reliever_index]][2] <- as.numeric(home_team_lineup[[4]][[home_reliever_index]][2]) + result[[3]]-outs
              home_reliever_outs <- home_reliever_outs + result[[3]]-outs
            }
            
            outs <- result[[3]]
            #print(paste("OUTS:", outs))
            if(PA=='Strikeout'){
              if(current_home_pitcher==2 | current_home_pitcher==5){
                home_team_lineup[[current_home_pitcher]][6] <- as.numeric(home_team_lineup[[current_home_pitcher]][6]) + 1
              }else{
                home_team_lineup[[4]][[home_reliever_index]][6] <- as.numeric(home_team_lineup[[4]][[home_reliever_index]][6]) + 1
              }
              
            }
            
            
            
          }else{
            result <-base_runners(PA, on_base,outs)
            on_base <- result[[2]]
            runs <- runs+ result[[1]]
            if(PA=='Walk'){
              if(current_home_pitcher==2 | current_home_pitcher ==5){
                home_team_lineup[[current_home_pitcher]][5] <- as.numeric(home_team_lineup[[current_home_pitcher]][5]) + 1
              }else{
                home_team_lineup[[4]][[home_reliever_index]][5] <- as.numeric(home_team_lineup[[4]][[home_reliever_index]][5]) + 1
              }
              
            }else{
              if(current_home_pitcher==2 | current_home_pitcher ==5){
                home_team_lineup[[current_home_pitcher]][4] <- as.numeric(home_team_lineup[[current_home_pitcher]][4]) + 1
              }else{
                home_team_lineup[[4]][[home_reliever_index]][4] <- as.numeric(home_team_lineup[[4]][[home_reliever_index]][4]) + 1
              }
              
            }
            
          }
          
          
          if(away_index==9){
            away_index <- 1
          }else{
            away_index <- away_index+1
          }
          
          if(outs==3){
            away_score <- append(away_score, runs)
            runs <- 0
            outs <- 0
            on_base <- c(F,F,F)
            top_of_inning<-FALSE
            break
          }
          
        }
        
        if(inning==9 & sum(home_score)>sum(away_score)){
          break
        }
        
      }
      if(top_of_inning==FALSE){
        #print(paste("Bottom of Inning", inning))
        while(TRUE){
          if(inning>=10){
            on_base <- c(F,T,F)
          }
          
          
          
          if(current_away_pitcher==2){
            if(as.numeric(away_team_lineup[[2]][2])+as.numeric(away_team_lineup[[2]][4])+as.numeric(away_team_lineup[[2]][5]) >29 |
               as.numeric(away_team_lineup[[2]][3])>=6 | (innings_pitched(as.numeric(away_team_lineup[[2]][2]))/as.numeric(away_team_lineup[[2]][3]) <= .8 & inning >=5) |
               (innings_pitched(as.numeric(away_team_lineup[[2]][2]))/as.numeric(away_team_lineup[[2]][3]) <= .5 & inning >=7)){
              current_away_pitcher = 4
            }
          }else if(current_away_pitcher==5){
            if(as.numeric(away_team_lineup[[5]][3])>=2 | as.numeric(away_team_lineup[[5]][2])>=6 | as.numeric(away_team_lineup[[2]][4])+as.numeric(away_team_lineup[[2]][5]) >=4){
              current_away_pitcher = 4
            }
          }else if(current_away_pitcher==4){
            if(innings_pitched(as.numeric(away_team_lineup[[4]][[away_reliever_index]][2]))>=2 | away_team_lineup[[4]][[away_reliever_index]][3]>=2 | 
               as.numeric(away_team_lineup[[4]][[away_reliever_index]][4])+as.numeric(away_team_lineup[[4]][[away_reliever_index]][5])>=3){
              if(away_reliever_index+1 <= length(away_team_lineup[[4]])){
                away_reliever_index <- away_reliever_index+1
                away_reliever_outs <- 0
              }
            }
          }
          
          if((inning==9|inning==10) & sum(away_score)-sum(home_score)<=3 & sum(away_score)-sum(home_score)>0 & as.numeric(away_team_lineup[[2]][2])+as.numeric(away_team_lineup[[2]][4])+as.numeric(away_team_lineup[[2]][5])>0){
            current_away_pitcher = 5
          }
          
          if(current_away_pitcher==2|current_away_pitcher==5){
            PA <- at_bat(away_team_lineup[[current_away_pitcher]][1],home_team_lineup[[3]][[home_index]][1])
          }else{
            PA <- at_bat(away_team_lineup[[4]][[away_reliever_index]][1],home_team_lineup[[3]][[home_index]][1])
          }
          
          
          
          if(length(home_team_lineup[[3]][[home_index]])==1){
            home_team_lineup[[3]][[home_index]]<-append(home_team_lineup[[3]][[home_index]],0)
          }
          home_team_lineup[[3]][[home_index]]<-append(home_team_lineup[[3]][[home_index]],PA)
          
          #print(paste("Batter: ", home_team_lineup[[3]][[home_index]][1], " in the ", home_index, "spot"))
          #print(PA)
          
          
          
          if(PA=='Strikeout'|PA=='Groundout'|PA=='Lineout'|PA=='Flyout'|PA=='Pop Up'){
            result <- base_runners(PA, on_base, outs)
            on_base <- result[[2]]
            runs <- runs + result[[1]]
            if(current_away_pitcher==2 | current_away_pitcher==5){
              away_team_lineup[[current_away_pitcher]][2] <- as.numeric(away_team_lineup[[current_away_pitcher]][2]) + result[[3]]-outs
            }else{
              away_team_lineup[[4]][[away_reliever_index]][2] <- as.numeric(away_team_lineup[[4]][[away_reliever_index]][2]) + result[[3]]-outs
              away_reliever_outs <- away_reliever_outs + result[[3]]-outs
            }
            
            outs <- result[[3]]
            #print(paste("OUTS:", outs))
            if(PA=='Strikeout'){
              if(current_away_pitcher==2 | current_away_pitcher==5){
                away_team_lineup[[current_away_pitcher]][6] <- as.numeric(away_team_lineup[[current_away_pitcher]][6]) + 1
              }else{
                away_team_lineup[[4]][[away_reliever_index]][6] <- as.numeric(away_team_lineup[[4]][[away_reliever_index]][6]) + 1
              }
              
            }
            
          }else{
            result <-base_runners(PA, on_base,outs)
            
            on_base <- result[[2]]
            runs <- runs+ result[[1]]
            if(PA=='Walk'){
              if(current_away_pitcher==2 | current_away_pitcher==5){
                away_team_lineup[[current_away_pitcher]][5] <- as.numeric(away_team_lineup[[current_away_pitcher]][5]) + 1
              }else{
                away_team_lineup[[4]][[away_reliever_index]][5] <- as.numeric(away_team_lineup[[4]][[away_reliever_index]][5]) + 1
              }
              
            }else{
              if(current_away_pitcher==2 | current_away_pitcher==5){
                away_team_lineup[[current_away_pitcher]][4] <- as.numeric(away_team_lineup[[current_away_pitcher]][4]) + 1
              }else{
                away_team_lineup[[4]][[away_reliever_index]][4] <- as.numeric(away_team_lineup[[4]][[away_reliever_index]][4]) + 1
              }
              
              
            }
          }
          
          if(home_index==9){
            home_index <- 1
          }else{
            home_index <- home_index+1
          }
          
          if(outs==3 | ((sum(home_score)+runs)>sum(away_score)&inning>=9)){
            if(inning>=9 & (sum(home_score)+runs-sum(away_score))>1 & PA!='Home Run'){
              if(runs==3){
                runs<-2
                PA <- "Double"
              }else if(runs==2){
                if(inning>=10){
                  PA <- "Single"
                }
                runs<-1
              }
            }
            home_score <- append(home_score, runs)
            runs <- 0
            outs <- 0
            
            
            on_base <- c(F,F,F)
            top_of_inning <- TRUE
            break
          }
          
        }
      }
      
      
      if(sum(away_score)!=sum(home_score) & inning >=9){
        break
      }
      
      inning <- inning +1
      
    }
    home_win <- TRUE
    if(sum(away_score)>sum(home_score)){
      home_win <- FALSE
    }
    wp_vec <- append(wp_vec, home_win)
    
  }
  return(sum(wp_vec))
}


#AL
#lineup structure: (Team name, starting pitcher, vector of vectors: (playername, stats), mrp pitchers, closing pitchers, possible pinch hitters)
dodgers_lineup <- list("Trea Turner","Max Muncy", "Mookie Betts","Justin Turner", "Corey Seager", "AJ Pollock", "Chris Taylor", "Will Smith", "Julio Urias")
dodgers_relievers <- list(c("Blake Treinen",0,0,0,0,0),c("Joe Kelly",0,0,0,0,0),c("Phil Bickford",0,0,0,0,0),c("Corey Knebel",0,0,0,0,0),c("Alex Vesia",0,0,0,0,0))
dodgers <- list('LAD',c('Julio Urias', 0,0,0,0,0), dodgers_lineup, dodgers_relievers ,c("Kenley Jansen",0,0,0,0,0))

giants_lineup <- list("Darin Ruf","Kris Bryant","Austin Slater", "Evan Longoria","Buster Posey", "Brandon Belt", "Thairo Estrada", "Mauricio Dubon", "Jay Jackson")
giants_relievers <- list(c("Jarlin Garcia",0,0,0,0,0), c("Jose Alvarez",0,0,0,0,0), c("Dominic Leone",0,0,0,0,0),c("Tony Watson",0,0,0,0,0),c("Zack Littell",0,0,0,0,0))
giants <- list(' SF', c('Jay Jackson', 0,0,0,0,0), giants_lineup, giants_relievers, c("Jake McGee",0,0,0,0,0))

astros_lineup <- list("Michael Brantley","Aldemys Diaz", "Alex Bregman","Yordan Ãlvarez","Yuli Gurriel", "Carlos Correa", "Kyle Tucker", "Martin Maldonado", "Framber Valdez")
astros_relievers <- list(c("Kendall Graveman",0,0,0,0,0), c("Ryne Stanek",0,0,0,0,0), c("Yimi Garcia",0,0,0,0,0), c("Phil Maton",0,0,0,0,0),c("Pedro Baez",0,0,0,0,0))
astros <- list('HOU', c('Framber Valdez', 0,0,0,0,0), astros_lineup, astros_relievers, c("Ryan Pressly",0,0,0,0,0))

padres_lineup <- list("Fernando Tatis Jr.","Manny Machado","Jake Cronenworth","Tommy Pham", "Wil Myers","Adam Frazier", "Austin Nola", "Jurickson Profar","Joe Musgrove")
padres_relievers <-list(c("Daniel Hudson",0,0,0,0,0), c("Emilio Pagan",0,0,0,0,0), c("Dinelson Lamet",0,0,0,0,0),c("Austin Adams",0,0,0,0,0),c("Pierce Johnson",0,0,0,0,0))
padres <- list('SDP', c('Joe Musgrove',0,0,0,0,0), padres_lineup, padres_relievers, c('Mark Melancon',0,0,0,0,0))

```

## Simulation Overview
baseball_game() is the function that simulates the baseball game.
After every at bat, win_probability_calc() is called, and simulates from the end of that at bat to the end of the game 1000 times. The resulting outcomes are stored in a vector, then returned to the main function where they are added to the dataframe.

The baseball_game() prints a box score of the simulated game, then returns the resulting data frame.
```{r warning=FALSE,comment=''}
astros_vs_padres <- baseball_game(padres, astros)
```

Here is the resulting data frame of this specific game simulation.
```{r warning=FALSE,comment=''}
astros_vs_padres
```
## Plotting the Data

Here is a plot of the resulting win probabilities, where the brown color is the Padres, and the orange color is the Astros
```{r echo=TRUE}
ggplot(astros_vs_padres, aes(x = batters_faced)) + geom_line(aes(y=home), color = 'tan4', lwd = 1.2) + geom_line(aes(y=away), color = 'darkgoldenrod1', lwd = 1.2) + scale_x_continuous(n.breaks = 9) + xlab("Total Batters Faced") + ylab("Win Percentage")
```

